Implications of uniformly distributed, empirically informed priors for phylogeographical model selection: A reply to Hickerson et al.

### 2014-02-19 manuscripts/dpp-msbayes/dpp-msbayes.tex
Updating title page metadata for dpp manuscript.
Defining variables to preserve values for title page data, so they
can be used beyond the title page.
Updating acknowledgements in both manuscripts.

\newcommand{\msTitle}{An Improved Approximate-Bayesian Model-choice Method for
    Estimating Shared Evolutionary History \xspace}

@@

\title{\msTitle}

@@

\section{Acknowledgments}
J.\ Oaks thanks the National Science Foundation for supporting this work (DEB
1011423 and DBI 1308885).
J.\ Oaks was also supported by the University of Kansas (KU) Office of Graduate
Studies, Society of Systematic Biologists, Sigma Xi Scientific Research
Society, KU Department of Ecology and Evolutionary Biology, and the KU
Biodiversity Institute.

>>>>

\title{An Improved Approximate-Bayesian Model-choice Method for Estimating
Shared Evolutionary History}

\makeatletter
\let\msTitle\@title
\let\msAuthor\@author
\let\msDate\@date
\makeatother

@@

@@

\section{Acknowledgments}
I am greatful to Melissa Callahan, Mark Holder, Emily McTavish, Daniel Money,
Jordan Koch, and Adam Leach\'{e} for insightful comments that greatly improved
this work.
I thank the National Science Foundation for supporting this work (DEB
1011423 and DBI 1308885).
This work was also supported by the University of Kansas (KU) Office of Graduate
Studies, Society of Systematic Biologists, Sigma Xi Scientific Research
Society, KU Department of Ecology and Evolutionary Biology, and the KU
Biodiversity Institute.
I also thank Mark Holder, the KU Information and Telecommunication Technology
Center, KU Computing Center, and the iPlant Collaborative for the computational
support necessary to conduct the analyses presented herein.

### 2014-02-19 manuscripts/reply/reply.tex
Updating acknowledgements in both manuscripts.

\section{Acknowledgments}
We thank Jake Esselstyn for insightful comments that greatly improved this
work.
J.\ Oaks thanks the National Science Foundation for supporting this work (DEB
1011423 and DBI 1308885).
J.\ Oaks was also supported by the University of Kansas (KU) Office of Graduate
Studies, Society of Systematic Biologists, Sigma Xi Scientific Research
Society, KU Department of Ecology and Evolutionary Biology, and the KU
Biodiversity Institute.

>>>>

\section{Acknowledgments}
We thank Melissa Callahan, Jake Esselstyn, Mark Holder, Emily McTavish, Daniel
Money, Jordan Koch, and Adam Leach\'{e} for insightful comments that greatly
improved this work.
J.\ Oaks thanks the National Science Foundation for supporting this work (DEB
1011423 and DBI 1308885).
J.\ Oaks was also supported by the University of Kansas (KU) Office of Graduate
Studies, Society of Systematic Biologists, Sigma Xi Scientific Research
Society, KU Department of Ecology and Evolutionary Biology, and the KU
Biodiversity Institute.
We also thank Mark Holder, the KU Information and Telecommunication Technology
Center, KU Computing Center, and the iPlant Collaborative for the computational
support necessary to conduct the analyses presented herein.
